### 2024-02-19 sections/0intro.tex
Add files via upload

\textbf{\Cref{ch:fact_alg} Factorization Algebras:} The third section introduces the concept of factorization algebras, together with its different variations, like prefactorization algebras and locally constant factorization algebras. Of these, the locally constant factorization algebras will be the ones that capture the different possible stratified structure that a manifold can have, and they will be a large focus of the work. The definitions of these will not be novel. They can be found in the works \cite{cg2016}, \cite{ginot2015} and even \cite{af_primer}. In fact, in the slightly different context of vertex algebras the idea can be traced back to \cite{bd2004}. However, all of the above works take a slightly different perspective in their presentation of the definitions, which we hope to unite in this work. The key result of this section is \cref{thm:disk_alg=lcfa}
%
\begin{theorem}
    There is an equivalence of $\infty$-categories between locally constant factorization algebras over a stratified manifold $M$ and $\disk_{/M}$-algebras
    %
    \begin{equation}
        \int: \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_M (\catC),
    \end{equation}
    %
    given by factorization homology,
\end{theorem}
%
as well as its corollary \cref{cor:disk_alg=falg} for the case of ordinary factorization algebras. These show that the $\infty$-operad governing factorization algebras can be taken to be the slice $\infty$-operad $\disk_{/M}$ (or $\disk[r]_{/M}$ for the ordinary case). We then introduce some operations that we can do with factorization algebras like the pushforward and restriction, as well as state a result for locally constant factorization algebras on product spaces. Finally, we will examine some examples of factorization algebras whose construction is known, specifically, locally constant factorization algebras on the intervals $(-1,1)$, $[-1,1)$ and $[-1,1]$ as well as Euclidean spaces $\mathbb{R}^n$ more generally.

\textbf{\Cref{ch:gluing_disk_alg} Collar-gluings and Disk Algebras:} The fourth section presents a novel result about the behavior of certain types of disk algebras under the operation of collar-gluing in the manifold variable. It essentially shows that one can reproduce a disk algebra on a stratified manifold if we know it on some particular pieces of it together with the data of how to glue them. Formally, we have
%
\begin{theorem}
    Given a collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$, the $\infty$-category of $\disk_{/M}$-algebras is equivalent to the pullback of $\infty$-categories
    %
    \begin{equation}
        \alg{\disk_{/M}} (\catC) \simeq \alg{\disk_{/M_-}} (\catC) \bigtimes_{\alg{\disk_{/M_0 \times \mathbb{R}}} (\catC)} \alg{\disk_{/M_+}} (\catC).
    \end{equation}
\end{theorem}
%
Together with the results of the previous section this gluing holds for locally constant factorization algebras too, and it hugely expands the number of manifolds for which the $\infty$-category of locally constant factorization algebras can be specified. As a small example, it gives a way work on the spheres $S^n$.

\textbf{\Cref{ch:classif_defect_mfld} Classifying $\lcfa$s on Defect Manifolds:} The fifth section focuses on the stratified structure and gives a way to express what effect this has on the locally constant factorization algebras. Specifically, we look the data of a smooth manifold $M$ with a distinguished, properly embedded submanifold $\sigma$ (also known as a defect) as the data of a stratified manifold $M_\Sigma$. We will show that, along with giving algebras associated to the different pieces, locally constant factorization algebras on these manifolds, in some sense, also encode a module structure associated with $\Sigma$.

>>>>

\textbf{\Cref{ch:fact_alg} Factorization Algebras:} The third section introduces the concept of factorization algebras, together with its different variations, like prefactorization algebras and locally constant factorization algebras. Of these, the locally constant factorization algebras will be the ones that capture the different possible stratified structure that a manifold can have, and they will be a large focus of the work. The definitions of these will not be novel. They can be found in the works \cite{cg2016}, \cite{ginot2015} and even \cite{af_primer}. In fact, in the slightly different context of vertex algebras the idea can be traced back to \cite{bd2004}. However, all of the above works take a slightly different perspective in their presentation of the definitions, which we hope to unite in this work. The key result of this section is \cref{thm:disk_alg=lcfa}:
%
\begin{theorem}
    There is an equivalence of $\infty$-categories between locally constant factorization algebras over a stratified manifold $M$ and $\disk_{/M}$-algebras
    %
    \begin{equation}
        \int: \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_M (\catC),
    \end{equation}
    %
    given by factorization homology,
\end{theorem}
%
as well as its \cref{cor:disk_alg=falg} for the case of ordinary factorization algebras. These show that the $\infty$-operad governing factorization algebras can be taken to be the slice $\infty$-operad $\disk_{/M}$ (or $\disk[r]_{/M}$ for the ordinary case). We then introduce some operations that we can do with factorization algebras like the pushforward and restriction, as well as state a result for locally constant factorization algebras on product spaces. Finally, we will examine some examples of factorization algebras whose construction is known, specifically, locally constant factorization algebras on the intervals $(-1,1)$, $[-1,1)$ and $[-1,1]$ as well as Euclidean spaces $\mathbb{R}^n$ more generally.

\textbf{\Cref{ch:gluing_disk_alg} Collar-gluings and Disk Algebras:} The fourth section presents a novel result about the behavior of certain types of disk algebras under the operation of collar-gluing in the manifold variable. It essentially shows that one can reproduce a disk algebra on a stratified manifold if we know it on some particular pieces of it together with the data of how to glue them. Formally, we have
%
\begin{theorem}
    Given a collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$, the $\infty$-category of $\disk_{/M}$-algebras is equivalent to the pullback of $\infty$-categories
    %
    \begin{equation}
        \alg{\disk_{/M}} (\catC) \simeq \alg{\disk_{/M_-}} (\catC) \bigtimes_{\alg{\disk_{/M_0 \times \mathbb{R}}} (\catC)} \alg{\disk_{/M_+}} (\catC).
    \end{equation}
\end{theorem}
%
Together with the results of the previous section this gluing holds for locally constant factorization algebras too, and it hugely expands the number of manifolds for which the $\infty$-category of locally constant factorization algebras can be specified. As a small example, it gives a way to work on all higher spheres $S^n$, of which, only the circle has been described to date.

\textbf{\Cref{ch:classif_defect_mfld} Classifying $\lcfa$s on Defect Manifolds:} The fifth section focuses on the stratified structure and gives a way to express what effect this has on the locally constant factorization algebras. Specifically, we look at the data of a smooth manifold $M$ with a distinguished, properly embedded submanifold $\Sigma$ (also known as a defect) as the data of a stratified manifold $M_\Sigma$. We will show that, along with giving algebras associated to the different pieces, locally constant factorization algebras on these manifolds, in some (precise) sense, also encode a module structure associated with $\Sigma$.

### 2024-02-19 sections/4gluing.tex
Add files via upload

@@

@@

\begin{example}
    In \cref{ch:classif_defect_mfld} we will see that fiber bundles are important for the classification of some stratified manifolds. Here we will look at line bundles over the circle as a toy example, namely, the cylinder $C$ and M\"obius band $M$. The cylinder, as a trivial fiber bundle, is isomorphic to the product space $S^1 \times \mathbb{R}$. By \cref{prop:exp_of_products_lc} together with the results of \cref{ex:reproduce_lcfas_on_S1}, locally constant factorization algebras on it are given by $\mathbb{E}_2$-algebras together with an $\mathbb{E}_1$-self-equivalence
    %
    \begin{align}
        \lcfa_C (\catC) \simeq \aut_{\mathbb{E}_1} (\alg{\mathbb{E}_2} (\catC)).
    \end{align}

@@

%\begin{example}{\color{red} GO TO LATER CHAPTER}
%    We have an immediate simplification of the result we saw in \cref{thm:ginot_classif_Rn*}, because its right-hand side is of the exact form to be a collar-gluing. Namely, it's the collar-gluing which, somewhat trivially, exhibits $\mathbb{R}^n_*$ as $ \cong \mathbb{R}^n_* \coprod_{\mathbb{R}^n \setminus \{0\}} \mathbb{R}^n \setminus \{0\}$. The result then simplifies to
%    %
%    \begin{equation}
%        \mathsf{Mod}^{\mathbb{E}_n} (\catC) \simeq \lcfa_{\mathbb{R}^n_*} (\catC). 
%    \end{equation}
%    %
%    This would confirm that the intuition we had from the 1 dimensional examples continues to hold in higher dimensions in a form that is easily parsable; introducing point defects on the manifold directly gives modules for the algebra.
%\end{example}

>>>>

\subsection{The Gluing Theorem}

@@

\subsection{Some Examples of Gluing}

@@

\begin{example}\label{ex:cylinder_mobius_band}
    In \cref{ch:classif_defect_mfld} we will see that fiber bundles are important for the classification of some stratified manifolds. Here we will look at line bundles over the circle as a toy example, namely, the cylinder $C$ and M\"obius band $M$. The cylinder, as a trivial fiber bundle, is isomorphic to the product space $S^1 \times \mathbb{R}$. By \cref{prop:exp_of_products_lc} together with the results of \cref{ex:reproduce_lcfas_on_S1}, locally constant factorization algebras on it are given by $\mathbb{E}_2$-algebras together with an $\mathbb{E}_1$-self-equivalence
    %
    \begin{align}
        \lcfa_C (\catC) \simeq \aut_{\mathbb{E}_1} (\alg{\mathbb{E}_2} (\catC)).
    \end{align}

@@

### 2024-02-19 sections/5classification.tex
Add files via upload

\section{Classifying \texorpdfstring{$\lcfa$}{FAlglc}s on Defect Manifolds}\label{ch:classif_defect_mfld}

@@

\begin{observation}
    For the purposes of the observation we will shorten notation to $\mathscr{D}_* := \disk (\mathsf{D}_{0 \subset n}^*)$. Since the defect is a point there can be at most one disk that contains it per morphism. Thus, the morphism spaces to consider are
    %
    \begin{align}
        &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n),& &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n_*)& &\mathrm{and}& &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i} \sqcup \mathbb{R}^n_*, \mathbb{R}^n_*).&
    \end{align}
    %
    The first of these is equivalent to the space $\mathsf{Emb}^*((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n)$ of framed open embeddings, which makes it is obvious that restricting to non-defect disks would give the data of an $\mathbb{E}_n$-algebra. This is related to \cref{lem:ff_functor_to_refinement}, which says that forgetting the stratification results in obtaining a full $\infty$-subcategory of locally constant factorization algebras. When $i=0$, the third space above is equivalent to a point, which makes it clear that restricting exclusively to pointed disks $\mathbb{R}^n_*$ would give rise to plain objects\footnote{We've omitted mentioning the fact that, because of morphisms like $\emptyset \xrightarrow{} U$, all of the above algebraic objects will be pointed. We have done this to avoid confusion with the use of pointed in the sense of a point defect of the space.} (or $\mathbb{E}_0$-algebras).

    The structure that connects these two algebras is encoded in the rest of the morphism spaces. In fact the second and third space above are equivalent,
    %
    \begin{equation}
        \mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n_*) \simeq \mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i} \sqcup \mathbb{R}^n_*, \mathbb{R}^n_*) \simeq \mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\}),
    \end{equation}
    %
    for all $i \in \mathbb{N}$, where $\mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\})$ is the space of framed embeddings of $i$ $n$-dimensional disks into the punctured $\mathbb{R}^n$.

@@

\begin{theorem}
    Let $n$ be bigger than 1. There is an equivalence between the $\infty$-category of locally constant factorization algebras on $\mathbb{R}^n_*$ and the $\infty$-category of $\mathbb{E}_n$-modules that fits into the commutative diagram
    %
    \begin{equation}
        \begin{tikzcd}
            \mathsf{Mod}^{\mathbb{E}_n} (\catC) \arrow[r, "\simeq"] \arrow[d] & \lcfa_{\mathbb{R}^n_*} (\catC) \arrow[d, "\cref{lem:ff_functor_to_refinement}"] \\
            \alg{\mathbb{E}_n} (\catC) \arrow[r, "\simeq"] & \lcfa_{\mathbb{R}^n} (\catC).
        \end{tikzcd}
    \end{equation}
\end{theorem}

@@

\begin{proof}
    Since $\mathsf{Mod}^{\mathbb{E}_n}$ is fibered over $\alg{\mathbb{E}_n}$, with fibers $\mathsf{Mod}^{\mathbb{E}_n}_A$ for $A$ an $\mathbb{E}_n$-algebra
\end{proof}

%\begin{theorem}
%    Let $n$ be bigger than 1. There is an equivalence between the $\infty$-category of $\mathbb{E}_n$-modules and the $\infty$-category of locally constant factorization algebras on $\mathbb{R}^n_*$
%    %
%    \begin{equation}
%        \mathsf{Mod}^{\mathbb{E}_n} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\mathbb{R}^n_*} (\catC).
%    \end{equation}
%\end{theorem}

%\begin{proof}
%    We immediately remark that \cite[lem.2.13]{francis2013} says that the universal enveloping algebra $U_A$ of an algebra $A \in \alg{\mathscr{O}} (\catC)$ is given as the value on $*$ of the left Kan extension of $A$ along the functor $\psi: \mathscr{O} \xrightarrow{} \mathscr{O}_*$ that adds a basepoint. Namely, this is the functor that adds a basepoint to objects and on morphism spaces it sends a map to its extension as a basepoint preserving map. We will argue that this functor is exactly the functor {\color{red} UNFINISHED}
%\end{proof}

%The study of these was undertaken in \cite{ginot2015}. There it was shown that

%\begin{theorem}[{\cite[cor.8]{ginot2015}}]\label{thm:ginot_classif_Rn*}
%    Let $n$ be bigger than 1. There is an equivalence between the $\infty$-categories of $\mathbb{E}_n$-modules and the pullback
%    %
%    \begin{equation}
%        \mathsf{Mod}^{\mathbb{E}_n} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\mathbb{R}^n_*} (\catC) \bigtimes_{\lcfa_{\mathbb{R}^n \setminus \{ 0\} } (\catC)} \lcfa_{\mathbb{R}^n} (\catC).
%    \end{equation}
%\end{theorem}

%\begin{remark}
%    The version of \cref{thm:ginot_classif_Rn*} cited above is different from the one appearing in the original reference. \cite[cor.8]{ginot2015}, as stated, requires the homotopy pullback, however examining its proof and the later \cite[cor.9]{ginot2015} implies that the correct statement that has been proven is as written above.
%\end{remark}

@@

Locally, near the defect, the locally constant factorization algebra is, of course, going to look like a locally constant factorization algebra over $\mathbb{R}^{d \subset n}$. However, it is possible that the global topology introduces some twisting of this local understanding. Due to \cref{cor:gluing_lcfas}, in any particular case, it's possible that we can find some list of collar-gluings that reduce the problem down to the local case, but this doesn't tell us anything about the general structure. Despite this, there is a particular collar-gluing that is the obvious first step if we're looking at a general manifold $M_\Sigma$. We will now describe this.

@@

By .... $\mathsf{C}(\pi)$ is always a bundle over $\Sigma$, fibered over basics. In the special case that $\Sigma$ is a stratum, $\mathsf{C}(\pi)$ is even a fiber bundle with fiber $\mathbb{R}^{n-d}_*$. Thus, the classification comes down to the classification of locally constant factorization algebras on stratified fiber bundles.

There is a special case that we can already tackle, which is the case of framed manifolds. This is because, as discussed in \cref{def:framed_d_under_n_structure}, $\mathsf{D}_{d \subset n}^*$-manifolds come with a trivialization of the normal bundle of the distinguished submanifold $\Sigma$. This, in turn implies a trivialization for $\mathsf{C}(\pi)$ as a bundle over $\Sigma$ with typical fiber $\mathbb{R}^{n-d}_*$, i.e. there is an isomorphism
%
\begin{equation}
    \mathsf{C}(\pi) \cong \Sigma \times \mathbb{R}^{n-d}_*.
\end{equation}

However, \cref{prop:exp_of_products_lc} already gives us a way to classify locally constant factorization algebras on product spaces, if we know them on the product components. Having classified locally constant factorization algebras on the pointed Euclidean space in \cref{thm:ginot_classif_Rn*}, we already have the result that
%
\begin{equation}
    \lcfa_{\mathsf{C}(\pi)} (\catC) \simeq \mathsf{Mod}^{\mathbb{E}_{n-d}} (\lcfa_{\Sigma} (\catC)).
\end{equation}

Going from $\mathsf{C}(\pi)$ to $M_{\Sigma}$ we use the fact that the link is also trivialized, as already mentioned above, which tells us that
%
\begin{equation}
    \lcfa_{\mathsf{L}_{\Sigma} \times \mathbb{R}} (\catC) \simeq \lcfa_{\Sigma \times (\mathbb{R} \setminus \{0\})} (\catC),
\end{equation}
%
and finally, that
% 
\begin{equation}
    \lcfa_{M_\Sigma} (\catC) \simeq \lcfa_{M \setminus \Sigma} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \setminus \{0\}} (\lcfa_{\Sigma} (\catC))} \mathsf{Mod}^{\mathbb{E}_{n-d}} (\lcfa_{\Sigma} (\catC)).
\end{equation}

Apart from confirming our previous observations that what is encoded is an algebra away from the defect, and algebra on the defect and a module structure relating them, this now exactly specifies what that module structure should be given by.

%--------------

%One hint comes from the following construction:

%\begin{construction}\label{con:norm_map}
%    Using the maps
%    %
%    \begin{align}
%        &\mathsf{L}_{\Sigma} \times \hoint \xrightarrow{\pi \times \mathrm{id}} \Sigma \times \hoint &\Sigma \xrightarrow{\mathrm{id} \times 0} \Sigma \times \hoint,
%    \end{align}
%    %
%    the universal property of the pushout for $\mathsf{C}(\pi)$ defines for us a map
%    %
%    \begin{equation}
%        \mathsf{C}(\pi) \xrightarrow{\ \ n \ \ } \Sigma \times \hoint,
%    \end{equation}
%    %
%    which we call the \emph{fiberwise norm map}. We similarly, define for ease of notation $n^\circ := \pi \times \mathrm{id}: \mathsf{L}_{\Sigma} \times \mathbb{R} \rightarrow \Sigma \times \mathbb{R}$, as the restriction of $n$ to the interior.
%\end{construction}

%\begin{remark}
%    The reason for the name is most visible in the case of point defects, e.g. $M_{\Sigma} = \mathbb{R}^n_{*}$. In this case $\mathsf{C}(\pi) \cong \mathbb{R}^n_{*}$, $\Sigma \times \hoint \cong \hoint$, and the fiberwise norm map $n: \mathbb{R}^n_{*} \rightarrow \hoint$ from above is exactly the norm in the usual sense. When the defect is higher dimensional, the above construction takes the norm in each fiber hence the name fiberwise norm.
%\end{remark}

%\begin{lemma}\label{lem:n_is_bundle}
%    The fiberwise norm map $n: \mathsf{C}(\pi) \rightarrow \Sigma \times \hoint$ is a constructible bundle.
%\end{lemma}

%\begin{proof}
%    The pushout construction of $\mathsf{C}(\pi)$ and \cref{con:norm_map} make it obvious that the necessary restrictions of $\mathsf{C}(\pi)$ over the strata give bundles over $\Sigma$ and $\Sigma \times \mathbb{R}$, fulfilling the conditions.
%\end{proof}

%Using the result mentioned in %\cref{rem:hoint_times_X_conjecture} ..., about locally constant factorization algebras on $\hoint \times \Sigma$ results in:

%\begin{lemma}
%    The pushforward along the fiberwise norm map fits into a commutative diagram
%    %
%    \begin{equation}
%        \begin{tikzcd}[row sep = large, column sep = large]
%            \lcfa_{\mathsf{C}(\pi)} (\catC) \arrow[r, "n_*"] \arrow[d] & \mathsf{LMod} (\lcfa_{\Sigma} (\catC)) \arrow[d] \\
%            \lcfa_{\mathsf{L}_{\Sigma} \times \mathbb{R}} (\catC) \arrow[r, "n^{\circ}_*"] & \alg{\mathbb{E}_1} (\lcfa_{\Sigma} (\catC)).
%        \end{tikzcd}
%    \end{equation}
%\end{lemma}

%\begin{proof}
%    \Cref{lem:n_is_bundle} guarantees that the pushforward $n_*: \lcfa_{\mathsf{C}(\pi)} \rightarrow \lcfa_{\Sigma \times \hoint}$ exists at the level of locally constant factorization algebras. The mentioned \cref{rem:hoint_times_X_conjecture} together with \cref{prop:hoint_gives_modules} then provides the equivalence of the codomain of the pushforward with $\mathsf{LMod} (\lcfa_{\Sigma} (\catC))$. The vertical functors are simply restrictions away from the defect in each case, so that the commutativity if immediate.
%\end{proof}

%\begin{remark}
%    This lemma gives us the direction that defects in general will again be related to a kind of module structure of the algebras, but it does not provide the full classification. If we are able to describe locally constant factorization algebras on the space $\mathsf{C}(\pi)$ in full detail, then we would be able to reconstruct the locally constant factorization algebras on $M_{\Sigma}$.
%\end{remark}

>>>>

\section{Towards Classifying \texorpdfstring{$\lcfa$}{FAlglc} on Defect Manifolds}\label{ch:classif_defect_mfld}

@@

\begin{observation}\label{obs:explore_D*}
    For the purposes of the observation we will shorten notation to $\mathscr{D}_* := \disk (\mathsf{D}_{0 \subset n}^*)$. Since the defect is a point there can be at most one disk that contains it per morphism. Thus, the morphism spaces to consider are
    %
    \begin{align}
        &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n),& &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n_*)& &\mathrm{and}& &\mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i} \sqcup \mathbb{R}^n_*, \mathbb{R}^n_*).&
    \end{align}
    %
    The first of these is equivalent to the space $\mathsf{Emb}^*((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n)$ of framed open embeddings, which makes it is obvious that restricting to non-defect disks would give the data of an $\mathbb{E}_n$-algebra. This is related to \cref{lem:ff_functor_to_refinement}, which says that forgetting the stratification results in obtaining a full $\infty$-subcategory of locally constant factorization algebras. When $i=0$, the third space above is equivalent to a point, which makes it clear that restricting exclusively to pointed disks $\mathbb{R}^n_*$ would give rise to plain objects\footnote{We've omitted mentioning the fact that, because of morphisms like $\emptyset \xrightarrow{} U$, all of the above algebraic objects will be pointed. We have done this to avoid confusion with the use of pointed in the sense of a point defect of the space.} (or $\mathbb{E}_0$-algebras). The structure that connects these two algebras is encoded in the rest of the morphism spaces. In fact the second and third space above are equivalent,
    %
    \begin{equation}
        \mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n_*) \simeq \mathsf{Hom}_{\mathscr{D}_*} ((\mathbb{R}^n)^{\sqcup i} \sqcup \mathbb{R}^n_*, \mathbb{R}^n_*) \simeq \mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\}),
    \end{equation}
    %
    for all $i \in \mathbb{N}$, where $\mathsf{Emb}^* ((\mathbb{R}^n)^{\sqcup i}, \mathbb{R}^n \setminus \{0\})$ is the space of framed embeddings of $i$ $n$-dimensional disks into the punctured $\mathbb{R}^n$.

    All of this is an elaboration of the fact that $\mathsf{D}_{0 \subset n}^*$ is equivalent to $\Delta^1 = \{0 \xrightarrow{} 1\}$ as $\infty$-categories (saying nothing about the right fibration to $\bsc$). Namely, the only nontrivial morphism is

@@

\begin{theorem}\label{thm:classif_Rn*}
    Let $n$ be bigger than 1. There is an equivalence between the $\infty$-category of locally constant factorization algebras on $\mathbb{R}^n_*$ and the $\infty$-category of $\mathbb{E}_n$-modules that fits into the commutative diagram
    %
    \begin{equation}
        \begin{tikzcd}
            \mathsf{Mod}^{\mathbb{E}_n} (\catC) \arrow[r, "\simeq"] \arrow[d] & \lcfa_{\mathbb{R}^n_*} (\catC) \arrow[d, "(\ref{lem:ff_functor_to_refinement})"] \\
            \alg{\mathbb{E}_n} (\catC) \arrow[r, "\simeq"] & \lcfa_{\mathbb{R}^n} (\catC).
        \end{tikzcd}
    \end{equation}
\end{theorem}

@@

\begin{proof}
    From \cref{eq:focus_on_disk_dn} we know that when $n > 1$ we have
    %
    \begin{equation}
        \lcfa_{\mathbb{R}^n_*} (\catC) \simeq \alg{\mathscr{D}_*} (\catC),
    \end{equation}
    %
    where we used the notation from \cref{obs:explore_D*}. Specializing \cref{thm:classif_disk_d_under_n*_alg} to the case at hand, and rewriting gives the left pullback square of the diagram
    %
    \begin{equation}
        \begin{tikzcd}
            \mathsf{Mod}^{\mathbb{E}_n}_A (\catC) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \alg{\mathscr{D}_*} (\catC) \arrow[d] \arrow[r, "\simeq"] & \lcfa_{\mathbb{R}^n_*} (\catC) \arrow[d, "(\ref{lem:ff_functor_to_refinement})"] \\
            * \arrow[r, "\{A\}"] & \alg{\mathbb{E}_n} (\catC) \arrow[r, "\simeq"] & \lcfa_{\mathbb{R}^n} (\catC).
        \end{tikzcd}
    \end{equation}
    %
    The right square obviously commutes by construction. Since, by definition, $\mathsf{Mod}^{\mathbb{E}_n} (\catC)$ is fibered over $\alg{\mathbb{E}_n} (\catC)$, with fibers $\mathsf{Mod}^{\mathbb{E}_n}_A (\catC)$ for $A$ an $\mathbb{E}_n$-algebra, the above diagram gives exactly the desired statement.
\end{proof}

\begin{remark}
    The study of locally constant factorization algebras on $\mathbb{R}^n_*$ was also undertaken in \cite[sec.6.3]{ginot2015}. \Cref{thm:classif_Rn*}, as it appears above, is slightly different in its statement compared to the corresponding \cite[cor.8]{ginot2015}. We believe that this is due to the fact that using the homotopy pullback is not what the proof provided in the reference actually does. The remaining discrepancy is then explained by our \cref{cor:gluing_lcfas}, which glues locally constant factorization algebras.
\end{remark}

@@

Locally, near the defect, the locally constant factorization algebra is, of course, going to look like a locally constant factorization algebra over $\mathbb{R}^{d \subset n}$. However, it is possible that the global topology introduces some twisting of this local understanding. Due to \cref{cor:gluing_lcfas} and the properties of stratified manifolds, in any particular case, it's possible to find some list of collar-gluings that reduce the problem down to the local case, but this doesn't tell us anything about the general structure. Despite this, there is a particular collar-gluing that is the obvious first step if we're looking at a general manifold $M_\Sigma$. We will now describe this.

@@

By \cite[ex.3.6.6]{aft_localstrut} $\mathsf{C}(\pi)$ is always a bundle over $\Sigma$, fibered over basics. For our particular setup this means that $\mathsf{C}(\pi)$ a fiber bundle over $\Sigma$ with typical fiber $\mathbb{R}^{n-d}_*$. Thus, the classification comes down to the classification of locally constant factorization algebras on stratified fiber bundles.

It is outside the scope of this work to finish the classification as outlined above. However, there is a special case that we can already tackle, which is the case of framed stratified manifolds. This is because, as discussed in \cref{def:framed_d_under_n_structure}, $\mathsf{D}_{d \subset n}^*$-manifolds come with a trivialization of the normal bundle of the distinguished submanifold $\Sigma$. This, in turn implies trivializations for $\mathsf{C}(\pi)$ and $\mathsf{L}_{\Sigma} \times \mathbb{R}$ as bundles over $\Sigma$ with typical fibers $\mathbb{R}^{n-d}_*$ and $S^{n-d-1} \times \mathbb{R}$, respectively. In other words, there are isomorphisms
%
\begin{align}
    &\mathsf{C}(\pi) \cong \Sigma \times \mathbb{R}^{n-d}_*& &\mathrm{and}& &\mathsf{L}_{\Sigma} \times \mathbb{R} \cong \Sigma \times S^{n-d-1} \times \mathbb{R}.&
\end{align}

However, \cref{prop:exp_of_products_lc} already gives us a way to classify locally constant factorization algebras on product spaces, if we know them on the product components. Having classified locally constant factorization algebras on the pointed Euclidean space in \cref{thm:classif_Rn*}, we already have the result that
%
\begin{equation}
    \lcfa_{\mathsf{C}(\pi)} (\catC) \simeq \mathsf{Mod}^{\mathbb{E}_{n-d}} (\lcfa_{\Sigma} (\catC)).
\end{equation}
%
Similarly, we also know that for the link we have
%
%
\begin{equation}
    \lcfa_{\mathsf{L}_{\Sigma} \times \mathbb{R}} (\catC) \simeq \lcfa_{\mathbb{R}^{n-d} \setminus \{ 0\} } (\lcfa_{\Sigma} (\catC)),
\end{equation}
%
exactly in such a way that the functor $\mathsf{Mod}^{\mathbb{E}_{n-d}} (\lcfa_{\Sigma} (\catC)) \xrightarrow{} \lcfa_{\mathbb{R}^{n-d} \setminus \{ 0\} } (\lcfa_{\Sigma} (\catC))$ is the one given by $\int_{S^{n-d-1}} -$, which to an algebra assigns its universal enveloping algebra.

Putting it all together, we have the equivalence
%
\begin{equation}
    \lcfa_{M_\Sigma} (\catC) \simeq \lcfa_{M \setminus \Sigma} (\catC) \bigtimes_{\lcfa_{\mathbb{R}^{n-d} \setminus \{0\}} (\lcfa_{\Sigma} (\catC))} \mathsf{Mod}^{\mathbb{E}_{n-d}} (\lcfa_{\Sigma} (\catC)).
\end{equation}
%
where the only functor that we haven't mentioned above is $\lcfa_{M \setminus \Sigma} (\catC) \xrightarrow{} \lcfa_{\mathbb{R}^{n-d} \setminus \{ 0\} } (\lcfa_{\Sigma} (\catC))$, which is given by restriction to the fattened link.

This description confirms the observation that what a locally constant factorization algebra on a defect manifold encodes is an algebra away from the defect, an algebra on the defect and a module structure relating them. Additionally, it exactly specifies what that module structure should be given by. In the case where the stratified manifold isn't framed we expect that the above structure will be `twisted' as seen in \cref{ex:cylinder_mobius_band} for the case of the M\"obius band.
